Methods to prioritise pop-up active transport infrastructure

### 2020-06-18 article.Rmd
Update figures

1. 'filtered permeability', where measures such as point closures or contraflow cycle lanes are used to design street networks in which routes for cyclists are faster and more direct than routes for drivers, e.g. as [shown](https://twitter.com/TowerHamletsNow/status/1257564043856019458) in [Tower Hamlets]

2. banning cars and to pedestrianise streets, as in New York's 'Open Streets' scheme [@litman_pandemicresilient_2020]
3. the reallocation of one or more lanes on wide roads to create pop-up cycleways and pavements [@orsman_covid_2020].
<!-- interventions to prevent through traffic, with interventions as part of Salford's ['Liveable Streets' project](https://salfordliveablestreets.commonplace.is/) being a prominent example  -->
<!-- (see [here](https://twitter.com/CatrionaSwanson/status/1258322956595453952) for a photo illustrating this type of intervention) -->

@@

```{r commonplace, fig.cap="Screenshot from the website salfordliveablestreets.commonplace.is to support local responses to the COVID-19 pandemic, including the prioritisation of pop-up active transport infrastructure."}
# knitr::include_graphics("https://user-images.githubusercontent.com/1825120/81451234-ed82d200-917b-11ea-977d-fff1665378c5.png")
# download.file("https://user-images.githubusercontent.com/1825120/81451234-ed82d200-917b-11ea-977d-fff1665378c5.png", "saferstreets.png")
knitr::include_graphics("saferstreets.png")
```

@@

```{r load}
library(sf)
library(tidyverse)
library(tmap)
region_name = "West Yorkshire"
source("code/build.R")
if(!file.exists("rsf_leeds.Rds")) {
  u = "https://github.com/cyipt/popupCycleways/releases/download/0.1/rsf_leeds.Rds"
  download.file(u, "rsf_leeds.Rds")
}
r_original = readRDS("rsf_leeds.Rds")
if(!file.exists("rtid.csv")) {
  ur = "https://github.com/cyipt/popupCycleways/releases/download/0.1/rtid.csv"
  download.file(ur, "rtid.csv")
}
rtid = readr::read_csv("rtid.csv")
region = ukboundaries::leeds
tmap_mode("plot")
```

```{r parameters}
regexclude = "welling"
min_cycling_potential = 0
min_grouped_cycling_potential = 100
min_grouped_length = 500
city_centre_buffer_radius_small = 5000
city_centre_buffer_radius = 8000
city_centre_buffer_radius_large = 10000
city_centre = tmaptools::geocode_OSM("leeds", as.sf = TRUE)
city_centre_buffer_small = stplanr::geo_buffer(city_centre, dist = city_centre_buffer_radius_small)
city_centre_buffer = stplanr::geo_buffer(city_centre, dist = city_centre_buffer_radius)
city_centre_buffer_large = stplanr::geo_buffer(city_centre, dist = city_centre_buffer_radius_large)
```

>>>>

1. 'filtered permeability', where measures such as point closures or contraflow cycle lanes are used to design street networks in which routes for cyclists are faster and more direct than routes for drivers, e.g. as [shown](https://twitter.com/TowerHamletsNow/status/1257564043856019458) in [Tower Hamlets]
2. banning cars and to pedestrianise streets, as in New York's 'Open Streets' scheme [@litman_pandemicresilient_2020]
3. the reallocation of one or more lanes on wide roads to create pop-up cycleways and pavements [@orsman_covid_2020].
<!-- interventions to prevent through traffic, with interventions as part of Salford's ['Liveable Streets' project](https://salfordliveablestreets.commonplace.is/) being a prominent example  -->
<!-- (see [here](https://twitter.com/CatrionaSwanson/status/1258322956595453952) for a photo illustrating this type of intervention) -->

@@

```{r commonplace, fig.cap="Screenshot from the website salfordliveablestreets.commonplace.is to support local responses to the COVID-19 pandemic, including the prioritisation of pop-up active transport infrastructure."}
# knitr::include_graphics("https://user-images.githubusercontent.com/1825120/81451234-ed82d200-917b-11ea-977d-fff1665378c5.png")
# download.file("https://user-images.githubusercontent.com/1825120/81451234-ed82d200-917b-11ea-977d-fff1665378c5.png", "saferstreets.png")
knitr::include_graphics(c(
  "figures/saferstreets.png",
  "figures/widenmypath-bristol.png"
  ))
```

@@

```{r load}
library(sf)
library(tidyverse)
library(tmap)
tmap_mode("plot")
rtid = readr::read_csv("rtid.csv")
region = ukboundaries::leeds
```
